---
title: "Analysis"
---

```{r libraries}
library(tidyverse)
library(lubridate)
library(glue)
library(here)
library(janitor)
library(zoo)
library(cowplot)
library(ggthemes)

devtools::load_all()
```

**SLIDE 1** Opening Slide

**SLIDE 2** Data Processing

```{r customer}
customer <- readr::read_csv(file.path(here::here(), 'data/customer_overall_data.csv')) %>% 
  select(-contains('X')) %>% 
  clean_names() %>% 
  mutate(acquisition_date = as.Date(acquisition_date)) %>% 
  mutate(acquisition_channel = if_else(is.na(acquisition_channel), 'Unknown', acquisition_channel)) %>% 
  mutate(acquisition_device = if_else(is.na(acquisition_device), 'Unknown', acquisition_device)) %>% 
  group_by(customer_id) %>% 
  arrange(acquisition_date) %>% 
  slice(1) %>% 
  ungroup()
```

```{r funnel_data}
funnel <- readr::read_csv(file.path(here::here(), 'data/cust_funnel.csv')) %>% 
  clean_names() %>% 
  mutate(year_month = as.yearmon(paste0(year, '-', month)))
```

**SLIDE 3** Data Processing Steps

**SLIDE 4** Outline

**SLIDE 5** Section Opening - Customer acquisition analysis

**SLIDE 6** Number of unique customers by year

```{r year}
p <- customer %>% 
  mutate(acquisition_year = year(acquisition_date)) %>% 
  group_by(acquisition_year) %>% 
  tally() %>% 
  ungroup() %>% 
  ggplot(aes(x = as.character(acquisition_year), y = n, label = n)) +
  geom_col(color = 'deepskyblue2', fill = 'deepskyblue2') +
  geom_text(size = 4, vjust = -1, color = 'black') +
  ggtitle('Number of Customers Acquired by Year') +
  xlab('Year') +
  ylab('Number of Customers Acquired') +
  theme_bw() +
  theme(legend.position = 'none') +
  ylim(0, 130)

save_fig(p, '06_cust_by_year')
print(p)
```

**SLIDE 7** Number of customers acquired by channels

```{r acquisition_channel}
p <- customer %>% 
  group_by(acquisition_channel) %>% 
  tally() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = reorder(acquisition_channel, n), y = n, fill = acquisition_channel, label = n)) +
  geom_col() +
  coord_flip() +
  geom_text(hjust = -0.5, size = 4) +
  ggtitle('Number of Customers by Acquisition Channel') +
  xlab('Acquisition Channel') +
  ylab('Number of Customers') +
  ylim(0, 600) +
  theme_bw() +
  theme(legend.position = 'none') +
  theme(text = element_text(size = 14))

save_fig(p, '07_cust_by_acquisition_channel')
print(p)
```

**SLIDE 8**: Number of customers acquired by channels and years

```{r acquisition_channel_year_raw, fig.width=6, fig.height=4}
p <- customer %>% 
  mutate(acquisition_year = year(acquisition_date)) %>% 
  group_by(acquisition_year, acquisition_channel) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(`Acquisition Channel` = acquisition_channel) %>% 
  ggplot(aes(x = as.integer(acquisition_year), y = n)) +
  geom_line(aes(color = `Acquisition Channel`), size = 1.5) + 
  ggtitle('Acquisition Channel by Year and Channel') +
  xlab('Year') +
  ylab('Number of Customers Acquired') +
  theme_bw() +
  xlim(2003, 2015) +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  theme(text=element_text(size=15))

save_fig(p, '08A_cust_by_yearraw', width = 10, height = 8)
print(p)
```

```{r acquisition_channel_year_prct, fig.width=6, fig.height=4}
unique_cust_by_year <- customer %>% 
  mutate(acquisition_year = year(acquisition_date)) %>% 
  group_by(acquisition_year) %>% 
  tally() %>% 
  ungroup()

p <- customer %>% 
  mutate(acquisition_year = year(acquisition_date)) %>% 
  group_by(acquisition_year, acquisition_channel) %>% 
  tally() %>% 
  ungroup() %>% 
  left_join(unique_cust_by_year, by = 'acquisition_year') %>% 
  mutate(prct = n.x/n.y,
         `Acquisition Channel` = acquisition_channel) %>% 
  ggplot(aes(x = as.character(acquisition_year), y = prct, fill = `Acquisition Channel`, label = ifelse(
    # acquisition_channel %in% c('Search - Organic', 'Search - Paid'), scales::percent(prct, 1), NA
    !acquisition_channel %in% c(''), scales::percent(prct, 1), NA
  ))) +
  geom_col() +
  geom_text(position = position_stack(vjust = 0.5), size = 4) + 
  ggtitle('Percentage of Customers Acquired by Acquisition Channel, by Year') +
  xlab('Year') +
  ylab('Percentage of Customers Acquired') +
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(text=element_text(size=15))

save_fig(p, '08B_cust_by_year_prct', width = 10, height = 8)
print(p)
```

**SLIDE 9** Number of customers acquired by device

```{r acquisition_device}
p <- customer %>% 
  group_by(acquisition_device) %>% 
  tally() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  ggplot(aes(x = reorder(acquisition_device, n), y = n, fill = acquisition_device, label = n)) +
  geom_col() +
  coord_flip() +
  geom_text(hjust = -0.5, size = 4) +
  ggtitle('Number of Customers Acquired by Device') +
  xlab('Acquisition Device') +
  ylab('Number of Customers') +
  ylim(0, 850) +
  theme_bw() +
  theme(legend.position = 'none') +
  theme(text = element_text(size = 14))

save_fig(p, '09_cust_by_acquisition_device')
print(p)
```

**SLIDE 10**: Number of customers acquired by device and years

```{r acquisition_device_year_raw, fig.width=6, fig.height=4}
p <- customer %>% 
  mutate(acquisition_year = year(acquisition_date)) %>% 
  group_by(acquisition_year, acquisition_device) %>% 
  tally() %>% 
  ungroup() %>% 
  ggplot(aes(x = as.character(acquisition_year), y = n, fill = acquisition_device, label = n)) +
  geom_col() +
  geom_text(position = position_stack(vjust = 0.5), size = 3) +
  ggtitle('Acquisition Device by Year') +
  xlab('Year') +
  ylab('Number of Customers Acquired') +
  theme_bw() +
  theme(text = element_text(size = 14))

save_fig(p, '10_cust_by_device_raw', width = 10, height = 8)
print(p)
```

**SLIDE 11**: Summary and Recommendations

**SLIDE 12** Section Opening - SKU Class Analysis

**SLIDE 13** SKU Views and SKU Added to Cart by SKU Class

**SLIDE 14** SKU Purchases and Revenue by SKU Class

**SLIDE 15** Total SKU Views by Months

```{r fig.width = 6, fig.height = 3}
p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_viewed) %>% 
  group_by(year_month) %>% 
  summarise(total_views = sum(skus_viewed)) %>% 
  ggplot(aes(x = year_month, y = total_views)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_bw() +
  xlab('Month') +
  ylab('Total SKUs Viewed') +
  ggtitle('Total SKUs Viewed by Months') +
  theme(text = element_text(size = 14))

save_fig(p, '15A_total_views_month', width = 12, height = 6)
print(p)
```

```{r skus_viewed, fig.width = 8, fig.height = 3}
p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_viewed) %>% 
  spread(key = class_name, value = skus_viewed) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year_month) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup() %>% 
  gather(key = class, value = skus_viewed, -year_month) %>% 
  ggplot(aes(x = year_month, y = skus_viewed, color = class)) +
  geom_line(size = 1.5) + 
  theme_bw() +
  xlab('Month') +
  ylab('Number of SKU Views') +
  ggtitle('Number of SKUs Viewed by SKU Class by Months') +
  theme(text = element_text(size = 14))

save_fig(p, '15B_sku_time_analysis_view_by_yearmon.png', width = 14, height = 6)
print(p)
```

**SLIDE 16** Total SKU Added to Cart by Months

```{r fig.width = 6, fig.height = 3}
tmp <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_added_to_cart) %>% 
  group_by(year_month) %>% 
  summarise(total_atc = sum(skus_added_to_cart))

p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_added_to_cart) %>% 
  group_by(year_month) %>% 
  summarise(total_atc = sum(skus_added_to_cart)) %>% 
  ggplot(aes(x = year_month, y = total_atc)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_bw() +
  xlab('Month') +
  ylab('Total SKUs Added to Cart') +
  ggtitle('Total SKUs Added to Cart by Month') +
  theme(text = element_text(size = 14))

save_fig(p, '16A_total_atc_month', width = 12, height = 6)
print(p)
```

```{r skus_added_to_cart, fig.width = 8, fig.height = 3}
p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_added_to_cart) %>% 
  spread(key = class_name, value = skus_added_to_cart) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year_month) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup() %>% 
  gather(key = class, value = skus_added_to_cart, -year_month) %>% 
  ggplot(aes(x = year_month, y = skus_added_to_cart, color = class)) +
  geom_line(size = 1.5) +
  theme_bw()  +
  xlab('Month') +
  ylab('Number of SKUs Added to Cart') +
  ggtitle('Number of SKUs Added to Cart by SKU Class and Months') +
  theme(text = element_text(size = 14))

save_fig(p, '16B_sku_time_analysis_atc_by_yearmon.png', width = 14, height = 6)
print(p)
```

**SLIDE 17** Total SKU Purchased by Months

```{r fig.width = 6, fig.height = 3}
tmp <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_purchased) %>% 
  group_by(year_month) %>% 
  summarise(total_pur = sum(skus_purchased))

p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_purchased) %>% 
  group_by(year_month) %>% 
  summarise(total_pur = sum(skus_purchased)) %>% 
  ggplot(aes(x = year_month, y = total_pur)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_bw() +
  xlab('Month') +
  ylab('Total SKUs Purchased') +
  ggtitle('Total SKUs Purchased') +
  theme(text = element_text(size = 14))

save_fig(p, '17A_total_pur_month.png', width = 12, height = 6)
print(p)
```

```{r skus_purchased, fig.width = 8, fig.height = 3}
p <- funnel %>% 
  distinct(year_month, customer_id, class_name, skus_purchased) %>% 
  spread(key = class_name, value = skus_purchased) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year_month) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup() %>% 
  gather(key = class, value = skus_purchased, -year_month) %>% 
  ggplot(aes(x = year_month, y = skus_purchased, color = class)) +
  geom_line(size = 1.5) +
  theme_bw()  +
  xlab('Month') +
  ylab('Number of SKU Purchased') +
  ggtitle('Number of Items Purchased SKU Class and Months') +
  theme(text = element_text(size = 14))

save_fig(p, '17B_sku_time_analysis_purchased_by_yearmon.png', width = 14, height = 6)
print(p)
```

**SLIDE 18** Revenue by Months

```{r fig.width = 6, fig.height = 3}
tmp <- funnel %>% 
  distinct(year_month, customer_id, class_name, revenue_generated) %>% 
  group_by(year_month) %>% 
  summarise(total_atc = sum(revenue_generated))

p <- funnel %>% 
  distinct(year_month, customer_id, class_name, revenue_generated) %>% 
  group_by(year_month) %>% 
  summarise(total_rev = sum(revenue_generated)) %>% 
  ggplot(aes(x = year_month, y = total_rev)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_bw() +
  xlab('Month') +
  ylab('Total Revenue') +
  ggtitle('Total Revenue') +
  theme(text = element_text(size = 14))

save_fig(p, '18A_total_rev_month.png', width = 12, height = 6)
print(p)
```

```{r revenue_by_time, fig.width = 8, fig.height = 3}
p <- funnel %>% 
  distinct(year_month, customer_id, class_name, revenue_generated) %>% 
  spread(key = class_name, value = revenue_generated) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year_month) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup() %>% 
  gather(key = class, value = revenue_generated, -year_month) %>% 
  ggplot(aes(x = year_month, y = revenue_generated, color = class)) +
  geom_line(size = 1.5) +
  theme_bw()  +
  xlab('Month') +
  ylab('Total Revenue') +
  ggtitle('Total Revenue by Class and Month') +
  theme(text = element_text(size = 14))

save_fig(p, '18B_sku_time_analysis_rev_by_yearmon.png', width = 14, height = 6)
print(p)
```

**SLIDE 19** Section Summary and Recommendations

**SLIDE 20** Section Summary and Recommendations (Cont.)

**SLIDE 21** Section Opening - Funnel Analysis

**SLIDE 22**

**SLIDE 23**

**SLIDE 24:** View-to-Cart Ratio (Added to Cart / View) % by Months

```{r add_to_cart_from_view_all}
p <- funnel %>% 
  group_by(year_month) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  ungroup() %>% 
  distinct(year_month, skus_viewed, skus_added_to_cart) %>% 
  mutate(view_to_cart = skus_added_to_cart/skus_viewed) %>% 
  ggplot(aes(x = year_month, y = view_to_cart)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_hc() +
  xlab('Month') +
  ylab('View to Cart %') +
  ggtitle('Added to Cart As % of Views by Months') +
  theme(text = element_text(size = 14))

save_fig(p, '24_view_to_cart_by_months_all.png', width = 12, height = 6)
print(p)
```

**SLIDE 25:** View-to-Cart Ratio (Added to Cart / View) % by Class and Years

```{r add_to_cart_from_view}
view <- funnel %>% 
  mutate(year = year(year_month)) %>% 
  group_by(year, customer_id, class_name) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  distinct(year, customer_id, class_name, skus_viewed) %>% 
  spread(key = class_name, value = skus_viewed) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup()

add_to_cart <- funnel %>% 
  mutate(year = year(year_month)) %>% 
  group_by(year, customer_id, class_name) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  distinct(year, customer_id, class_name, skus_added_to_cart) %>% 
  spread(key = class_name, value = skus_added_to_cart) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup()

cart_from_view <- as_tibble(as.matrix(add_to_cart)[,-1]/as.matrix(view)[,-1])
cart_from_view$year <- add_to_cart$year

p <- cart_from_view %>% 
  gather(key = class, value = cart_from_view, -year) %>% 
  ggplot(aes(x = year, y = cart_from_view, fill = class)) +
  geom_col(position = 'dodge') +
  theme_bw() +
  xlab('Year') +
  ylab('View to Cart %') +
  ggtitle('Added to Cart As % of Views by Years') +
  theme(text = element_text(size = 14))

save_fig(p, '25_view_to_cart_by_years.png', width = 12, height = 6)
print(p)
```

**SLIDE 26:** Cart-to-Purchase Ratio (Purchase / Added to Cart) % by Months

```{r cart_to_purchase_all}
p <- funnel %>% 
  group_by(year_month) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  ungroup() %>% 
  distinct(year_month, skus_added_to_cart, skus_purchased) %>% 
  mutate(cart_to_purchase = skus_purchased/skus_added_to_cart) %>% 
  ggplot(aes(x = year_month, y = cart_to_purchase)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_hc() +
  xlab('Month') +
  ylab('Cart to Purchase %') +
  ggtitle('Purchase As % of Added to Cart by Months') +
  theme(text = element_text(size = 14))

save_fig(p, '26_cart_to_purchase_by_months_all.png', width = 12, height = 6)
print(p)
```

**SLIDE 27:** Cart-to-Purchase Ratio (Purchase / Added to Cart) % by Class and Years

```{r cart_to_purchase}
purchase <- funnel %>% 
  mutate(year = year(year_month)) %>% 
  group_by(year, customer_id, class_name) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  distinct(year, customer_id, class_name, skus_purchased) %>% 
  spread(key = class_name, value = skus_purchased) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup()

purchase_from_cart <- as_tibble(as.matrix(purchase)[,-1]/as.matrix(add_to_cart)[,-1])
purchase_from_cart$year <- purchase$year

p <- purchase_from_cart %>% 
  gather(key = class, value = purchase_from_cart, -year) %>% 
  ggplot(aes(x = year, y = purchase_from_cart, fill = class)) +
  geom_col(position = 'dodge') +
  theme_bw() +
  xlab('Year') +
  ylab('Cart to Purchase %') +
  ggtitle('Purchase As % of Added to Cart by Years') +
  theme(text = element_text(size = 14))

save_fig(p, '27_cart_to_purchase_by_years.png', width = 12, height = 6)
print(p)
```

**SLIDE 28:** (Revenue / Purchases) by Months

```{r revenue_per_order_all}
p <- funnel %>% 
  group_by(year_month) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  ungroup() %>% 
  distinct(year_month, skus_purchased, revenue_generated) %>% 
  mutate(revenue_per_order = revenue_generated/skus_purchased) %>% 
  ggplot(aes(x = year_month, y = revenue_per_order)) +
  geom_line(size = 1.5, color = 'deepskyblue2') + 
  theme_hc() +
  xlab('Month') +
  ylab('Revenue per Order') +
  ggtitle('Revenue per Order by Months') +
  theme(text = element_text(size = 14))

save_fig(p, '28_revenue_per_order_by_months_all.png', width = 12, height = 6)
print(p)
```

**SLIDE 29:** Revenue per Order by Class and Years

```{r revenue_per_order}
revenue <- funnel %>% 
  mutate(year = year(year_month)) %>% 
  group_by(year, customer_id, class_name) %>% 
  summarize(skus_viewed = sum(skus_viewed),
            skus_added_to_cart = sum(skus_added_to_cart),
            skus_purchased = sum(skus_purchased),
            revenue_generated = sum(revenue_generated)) %>% 
  distinct(year, customer_id, class_name, revenue_generated) %>% 
  spread(key = class_name, value = revenue_generated) %>% 
  mutate_all(replace_na, 0) %>% 
  group_by(year) %>% 
  summarize_at(vars(-customer_id), sum) %>% 
  ungroup()

revenue_per_purchase <- as_tibble(as.matrix(revenue)[,-1]/as.matrix(purchase)[,-1])
revenue_per_purchase$year <- revenue$year

p <- revenue_per_purchase %>% 
  gather(key = class, value = revenue_per_purchase, -year) %>% 
  ggplot(aes(x = year, y = revenue_per_purchase, fill = class)) +
  geom_col(position = 'dodge') +
  theme_bw() +
  xlab('Year') +
  ylab('Revenue per Order') +
  ggtitle('Revenue per Order by Years') +
  theme(text = element_text(size = 14))

save_fig(p, '29_revenue_per_order_by_years.png', width = 12, height = 6)
print(p)
```

**SLIDE 30** Section Summary and Recommendations




